Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-01 main.tex
Updates from Overleaf

%=================================================================
% pm-1174473
% Journal of Personalized Medicine, JPM
\documentclass[jpm,article,submit,moreauthors,pdftex]{Definitions/mdpi}
\maxdeadcycles=1000 % Output loop---200 consecutive dead cycles.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Tex
\usepackage{tikz-imagelabels} % for  tikz
\usepackage[]{caption} % bf
\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
\usepackage{outlines}
% mark in blue or red
\usepackage{xcolor}
\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}

@@

%\begin{MyColorPar}{red}
%\end{MyColorPar}

%\usepackage[upplemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
%...
%\usepackage{graphicx}
%\DeclareGraphicsExtensions{.pdf,.png} % for high-resolution PDF image
%\usepackage{hyperref}
\usepackage{xr}
% for xr in your preamble
% https://www.overleaf.com/learn/how-to/Cross_referencing_with_the_xr_package_in_Overleaf
\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

@@

%\usepackage{url}

@@

%%% for abbreviations, or acronyms
\usepackage[automake, acronym, nopostdot]{glossaries} 
\usepackage{glossary-inline}
%\setacronymstyle{long-short}
%\renewcommand*{\glossarysection}[2][]{} 
%\renewcommand*{\glossarysection}[2][]{\textbf{#1}: }
% for abbreviations environment
%\newcommand{\abbrlabel}[1]{\makebox[3cm][l]{\textbf{#1}\ \dotfill}}
\newenvironment{abbreviation}%{\begin{list}{}{\renewcommand{\makelabel}{\abbrlabel}}}{\end{list}}
% \newenvironment{<name>}[<number>][<default>]

\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed

@@

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2021}
\copyrightyear{2021}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{} 
\dateaccepted{} 
\datepublished{}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC). It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis. There is some optimization software for cutoff determination. However, the software's predetermined cutoffs are usually set at the median or quantiles of RNA sequencing value to perform the survival analyses. There are few clinicopathological features available on their pre-processed data sets.

We developed a workflow that includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
The independent HNSCC dataset has been used to validate this discovery.

Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes. After adjustment with confounders, we found that the clinical tumor stage and the surgical margin involvement are independent risk factors in patient survival. According to the resulting tables with Bonferroni adjusted P-value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, IL19, and FCGBP, are significantly associated with the patients' overall survival.
We suggest the transcriptomic analysis could help for biomarker discovery.
}

%Survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC). It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression. Usually, an optimization algorithm for cutoff determination has been set at the median or quantiles of RNA sequencing value.
%There are few clinicopathological features available on those pre-processed datasets. (feature selection or feature engineering issue)
% validated by the other HNSCC cohort:
%1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
%2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\

% row 20: The result showed ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of overall survival. Furthermore, the other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.

% Keywords
\keyword{
Head and Neck Squamous Cell Carcinoma (HNSCC);
%Genome Database\sep
the Cancer Genome Atlas (TCGA);
Transcriptomic Analysis;
%RNA-sequencing;
Survival Analysis;
Optimal Cutoff;
Effect Size;
%Tobacco\sep
%Cox Proportional Hazards\sep
%Tumor Aggressiveness\sep
%Rstudio\sep
CAMK2N1;
IL19;
FCGBP;
%Biomarker\sep % Discovery\sep
%Tumor Type-agnostic Therapy\sep
%Immuno-Oncology\sep
%Targeted Therapy\sep
%Systemic Therapy\sep
%Surgical Margin
%Holistic Cancer Care;
%Therapeutic Relationship;
Mindfulness Meditation
}

% I have a graphic abstract: graphic_abstract_pvalueTex.pdf
% National Cancer Institute. Changing the dressing on a patient’s neck. https://unsplash.com/photos/IrqLPsxemQ4?utm_source=unsplash&utm_medium=referral&utm_content=creditShareLink (1950).\cite{nci1950}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\globalcounter* % for paracol

\begin{document}
%\linenumbers
%\begin{paracol}{2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.
%\section{How to Use this Template}

%The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
%%

%\begin{figure}
%    \centering
%    \includegraphics[width=14cm]{graphic_abstract_pvalueTex.pdf}
%    \caption{(inset image courtesy of National Cancer Institute\cite{nci1950})}
%    \label{fig:my_label}
%\end{figure}

@@

Until the immuno-oncology era, \acrfull{ici} was introduced since 2014 for treating \acrshort{hnscc}\cite{Seiwert2014}\cite{Swanson2015}.
The \acrshort{ici} works on immune checkpoint molecules, including \acrfull{pd1}, \acrfull{ctla4}, \acrfull{tim3}, \acrfull{lag3}, \acrfull{tigit}, \acrfull{gitr}, and \acrfull{vista}\cite{Mei2020}.
The \acrshort{us} \acrshort{fda} has approved the anti-\acrshort{pd1} agents (e.g. pembrolizumab and nivolumab) as a monotherapy for the platinum-treated patients with recurrent or metastatic \acrshort{hnscc}\cite{Cramer2019}. 
According to the phase 3 KEYNOTE-048 study, \acrshort{pdl1} is a validated biomarker used in clinical guidance for candidate selection of pembrolizumab\cite{Burtness2019}\cite{Gavrielatou2020}.
However, because of the complexity of immune-tumor interaction, \acrshort{ici} has 20\% response rate to \acrfull{pdl1} expressed patients (over 50\% in \acrlong{ihc}, \acrshort{ihc} staining of \acrshort{hnscc})\cite{Swanson2015}\cite{Gavrielatou2020}.

@@

\begin{MyColorPar}{red}
\subsubsection{From TCGA to expression biomarkers} % from Answer 2-6 minor2
Usually, researchers developed an in-house workflow of gene expression analysis to find HNSCC biomarkers.
They have several genes that are differentially expressed between tumor and normal samples.
It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC

% Rstudio\cite{Loraine2015a}
Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019}\cite{Xu2021a} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.x. GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
% IRB: Patient samples were obtained under the protocol S-206/2011, approved by the Ethics Committee of Heidelberg University, with written informed consent from all participants.
%e.x. GSE30784: 167 HNSCC samples and 45 normal controls). 
They employed the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function. 
The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions.
%Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, String, or Cytoscape software programs\cite{Huang2019}\cite{Shen2019}.
Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows on gene expression analyses of the TCGA.
%The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software. Moreover, genes with degree $>= 25$ were selected as hub genes. Subsequently, module analysis (16) of the PPI network was performed using the Molecular Complex Detection (MCODE) tool of Cytoscape software, and GO and KEGG analysis of the modules was carried out using the DAVID database.
%a validation set and
%Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value $< 0.05$).
The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
%By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses. The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
The candidate genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
%, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
), GEPIA2021\cite{Li2021} (available at http://\\gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.
% GTEx https://gtexportal.org/home/; non-disease 54 tissues/organs
% GEPIA1/2 contact us: tangzefang@pku.edu.cn
Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.\\
\end{MyColorPar}

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{MyColorPar}{red}
TCGA HNSCC cohort has been applied for exploration of the biomarker candidate.
The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
The 967 genes were kept by criteria of unadjusted \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
%The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

@@

@@

% end of result

%Bulleted lists look like this:
%\begin{itemize}
%\item	First bullet;
%\item	Second bullet;
%\item	Third bullet.
%\end{itemize}

%Numbered lists can be added as follows:
%\begin{enumerate}
%\item	First item; 
%\item	Second item;
%\item	Third item.
%\end{enumerate}

%\subsection{Figures, Tables and Schemes}

%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

%\begin{figure}[H]
%\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
%\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
%\end{figure}

% The MDPI table float is called specialtable
%\begin{specialtable}[H] 
%\caption{This is a table caption. Tables %should be placed in the main text near to %the first time they are~cited.\label{tab1}}
%%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
%\begin{tabular}{ccc}
%\toprule
%\textbf{Title 1}	& \textbf{Title 2}	& %\textbf{Title 3}\\
%\midrule
%Entry 1		& Data			& Data\\
%Entry 2		& Data			& Data\\
%\bottomrule
%\end{tabular}
%\end{specialtable}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

%\subsection{Formatting of Mathematical Components}

%This is the example 1 of equation:

%\begin{equation}
%a = 1,
%\end{equation}

%the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

\end{paracol}
\nointerlineskip

@@

% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.

\begin{paracol}{2}
\linenumbers
\switchcolumn[1]

%Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
%\begin{Theorem}
%Example text of a theorem.
%\end{Theorem}

%% Example of a proof:
%\begin{proof}[Proof of Theorem 1]
%Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
%\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods} % 4

@@

% moved from line 363

%latex https://www.latex-tutorial.com/symbols/greek-alphabet/
%\subsection*{Linear regression in biomarker discovery}
Linear regression is useful as a concept in biomarker discovery.
A linear regression equation that relates a Y-variable to n X-variables is written as\\[1cm]
%\par
%Highlights
% https://quicklatex.com
\begin{flushleft}
% equation
%\begin{math}

>>>>

%=================================================================
\documentclass[jpm,article,submit,moreauthors,pdftex]{Definitions/mdpi} 
% pm-1174473
% Journal of Personalized Medicine, JPM

@@

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2021}
\copyrightyear{2021}
%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
%\hreflink{https://doi.org/} % If needed use \linebreak
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Tex
\maxdeadcycles=1000 % Output loop---200 consecutive dead cycles.

\usepackage{amsmath,amsfonts}
\usepackage{tikz-imagelabels} % for  tikz
\usepackage[]{caption} % bf
\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
\usepackage{outlines}
% mark in blue or red
\usepackage{xcolor}
\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}

@@

\usepackage{hyperref}
\usepackage{xr}
% for xr in your preamble
% https://www.overleaf.com/learn/how-to/Cross_referencing_with_the_xr_package_in_Overleaf
\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

@@

@@

%%% for abbreviations, or acronyms
\usepackage[automake, acronym, nopostdot]{glossaries} 
\usepackage{glossary-inline}
%\setacronymstyle{long-short}
%\renewcommand*{\glossarysection}[2][]{} 
%\renewcommand*{\glossarysection}[2][]{\textbf{#1}: }
% for abbreviations environment
%\newcommand{\abbrlabel}[1]{\makebox[3cm][l]{\textbf{#1}\ \dotfill}}
\newenvironment{abbreviation}

%%%%%%%%%%%%% Define abbreviation
\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed

@@

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}

@@

%%%%%%%%%%
% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC). It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis. There is some optimization software for cutoff determination. However, the software's predetermined cutoffs are usually set at the median or quantiles of RNA sequencing value to perform the survival analyses. There are few clinicopathological features available on their pre-processed data sets.
We developed a workflow that includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
The independent HNSCC dataset has been used to validate this discovery.
Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes. After adjustment with confounders, we found that the clinical tumor stage and the surgical margin involvement are independent risk factors in patient survival. According to the resulting tables with Bonferroni adjusted P-value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, IL19, and FCGBP, are significantly associated with the patients' overall survival.
We suggest the transcriptomic analysis could help for biomarker discovery.}

% Keywords
\keyword{Head and Neck Squamous Cell Carcinoma (HNSCC);
the Cancer Genome Atlas (TCGA); Transcriptomic Analysis; Survival Analysis; Optimal Cutoff; Effect Size; CAMK2N1; IL19; FCGBP; Mindfulness Meditation}

% I have a graphic abstract: graphic_abstract_pvalueTex.pdf
%\globalcounter* % for paracol

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{Instead of the abstract}
%\entrylink{The Link to this entry published on the encyclopedia platform.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%\begin{paracol}{2} % there is no this item here
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.
%\section{How to Use this Template}

%The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

@@

Until the immuno-oncology era, \acrfull{ici} was introduced since 2014 for treating \acrshort{hnscc}\cite{Seiwert2014}\cite{Swanson2015}.
The \acrshort{ici} works on immune checkpoint molecules, including \acrfull{pd1}, \acrfull{ctla4}, \acrfull{tim3}, \acrfull{lag3}, \acrfull{tigit}, \acrfull{gitr}, and \acrfull{vista}\cite{Mei2020}.
The \acrshort{us} \acrshort{fda} has approved the anti-\acrshort{pd1} agents (e.g. pembrolizumab and nivolumab) as a monotherapy for the platinum-treated patients with recurrent or metastatic \acrshort{hnscc}\cite{Cramer2019}. 
According to the phase 3 KEYNOTE-048 study, \acrshort{pdl1} is a validated biomarker used in clinical guidance for candidate selection of pembrolizumab\cite{Burtness2019}\cite{Gavrielatou2020}.
However, due to the complexity of immune-tumor interaction, \acrshort{ici} has 20\% response rate to \acrfull{pdl1} expressed patients (over 50\% in \acrlong{ihc}, \acrshort{ihc} staining of \acrshort{hnscc})\cite{Swanson2015}\cite{Gavrielatou2020}.

@@

\begin{MyColorPar}{red}
%\subsubsection{From TCGA to expression biomarkers} % from Answer 2-6 minor2
Usually, researchers developed an in-house workflow of gene expression analysis to find HNSCC biomarkers.
They have several genes that are differentially expressed between tumor and normal samples.
It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC

% Rstudio\cite{Loraine2015a}
Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019}\cite{Xu2021a} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.x. GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
% IRB: Patient samples were obtained under the protocol S-206/2011, approved by the Ethics Committee of Heidelberg University, with written informed consent from all participants.
%e.x. GSE30784: 167 HNSCC samples and 45 normal controls). 
They employed the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function. 
The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions.
%Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, String, or Cytoscape software programs\cite{Huang2019}\cite{Shen2019}.
Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows on gene expression analyses of the TCGA.
%The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software. Moreover, genes with degree $>= 25$ were selected as hub genes. Subsequently, module analysis (16) of the PPI network was performed using the Molecular Complex Detection (MCODE) tool of Cytoscape software, and GO and KEGG analysis of the modules was carried out using the DAVID database.
%a validation set and
%Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value \begin{equation}< 0.05 \end{equation}).
The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
%By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses. The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
The candidate genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
%, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
), GEPIA2021\cite{Li2021} (available at http://\\gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.
% GTEx https://gtexportal.org/home/; non-disease 54 tissues/organs
% GEPIA1/2 contact us: tangzefang@pku.edu.cn
Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.\\
\end{MyColorPar} % red

@@

\clearpage % end of Introduction

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{MyColorPar}{red}
TCGA HNSCC cohort has been applied for exploration of the biomarker candidate.
The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
The 967 genes were kept by criteria of unadjusted \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
%The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

@@

%%%%%%%%%%%%%
\end{paracol}
\nointerlineskip
%%%%%%%%%%%%% give wide full-paged tables

@@

% end of result
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

%This is the example 2 of equation:

@@

% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
%\begin{figure}[H]	
%\widefigure
%\includegraphics[width=15 cm]{Definitions/logo-mdpi}
%\caption{This is a wide figure.\label{fig2}}
%\end{figure}

\begin{paracol}{2}
\linenumbers
\switchcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%
\section{Discussion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{quote}
%This is an example of a quote.
%\end{quote}

\section{Materials and Methods} % 4

@@
